\RequirePackage{pdf14}
\documentclass{beamer}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[ngerman]{babel}
%\usepackage{paralist}
%\useoutertheme{infolines} 
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{color}
\usetheme{Warsaw}
\usecolortheme{crane}
\pagenumbering{arabic}
\def\thesection{\arabic{section})}
\def\thesubsection{\alph{subsection})}
\def\thesubsubsection{(\roman{subsubsection})}
\setbeamertemplate{navigation symbols}{}
\graphicspath{ {src/} {/home/jim/Pictures/} }

\definecolor{mygreen}{rgb}{0,0.6,0}
\definecolor{mygray}{rgb}{0.5,0.5,0.5}
\definecolor{mymauve}{rgb}{0.58,0,0.82}

\lstset{ %
  backgroundcolor=\color{white},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}
  basicstyle=\footnotesize,        % the size of the fonts that are used for the code
  breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
  breaklines=true,                 % sets automatic line breaking
  captionpos=b,                    % sets the caption-position to bottom
  commentstyle=\color{mygray},    % comment style
  deletekeywords={},            % if you want to delete keywords from the given language
  escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
  extendedchars=true,              % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8
  keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
  keywordstyle=\color{blue},       % keyword style
  language=PHP,                 % the language of the code
  morekeywords={class, function, return, protected, public, private, const, static, new, extends, namespace, null},            % if you want to add more keywords to the set
  numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
  numbersep=5pt,                   % how far the line-numbers are from the code
  numberstyle=\tiny\color{mygray}, % the style that is used for the line-numbers
  rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
  showspaces=false,                % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
  showstringspaces=false,          % underline spaces within strings only
  showtabs=false,                  % show tabs within strings adding particular underscores
  stepnumber=2,                    % the step between two line-numbers. If it's 1, each line will be numbered
  stringstyle=\color{mygreen},     % string literal style
  tabsize=2,                       % sets default tabsize to 2 spaces
  title=\lstname                   % show the filename of files included with \lstinputlisting; also try caption instead of title
}

\hypersetup{
	pdfauthor=Jim Martens,
	pdfstartview=Fit
}

\expandafter\def\expandafter\insertshorttitle\expandafter{%
	\raggedleft \insertframenumber\,/\,\inserttotalframenumber\;}

\begin{document}
\author{Jim 2martens}
\title{2martens Web Platform}
\date{October 2014}

	% Introduction
	\begin{frame}
		\titlepage
	\end{frame}
	
	% Motivation
	\begin{frame}{Motivation}
		\begin{itemize}
			\item Why do we need it?
			\item Such a thing already exists...
			\item If noone has done it yet, it has a reason...
			\item I am using already X, Y and Z and it works...
		\end{itemize}
		
		Well...
	\end{frame}
	
	\begin{frame}{Motivation}
		\begin{itemize}
			\item it's state-of-the-art
			\item it's extendable
			\item it's functional
			\item it's modular
			\item it's testable
			\item it's free
		\end{itemize}
		
		Enough of the buzz words, let's get serious
	\end{frame}	
	
	% Contents
	\begin{frame}{Agenda}
		\tableofcontents
	\end{frame}
	
	\section{Basics}
	\begin{frame}{Beginning}
		In the beginning was Symfony2. And it was good. There was Drupal as CMS but no real forum. Nor were there applications that were intercompatible from the get-go.
		
		The main reason being that Symfony2 is mostly used as a base for highly customized applications.
	\end{frame}
	
	\begin{frame}{Goal}
		Deliver a web-platform that provides core community functionality similar to the WoltLab Community Framework (WCF) and central features that are desperately needed for every modern web application.	
	\end{frame}
	
	\begin{frame}{Core Features}
		\begin{itemize}
			\item Administrator Control Panel (ACP)
			\item User and Group system
			\item Package system
			\item Style system
			\item Project system
		\end{itemize}
	\end{frame}
	
	\section{Details}
	\subsection{Approach}
	\begin{frame}{Comparisons}
		\begin{table}
			\begin{tabular}{l|r}
				Our feature & 3rdParty \\
				\hline
				ACP & Sonata Admin Bundle \\
				Package system & Composer \\
				User and Group system & FOSUserBundle \\
				Style system & Twitter Bootstrap/LESS
			\end{tabular}
		\end{table}
		
		\centering Why don't we use existing software?
	\end{frame}
	
	\begin{frame}{Comparisons}
		All these 3rdParty things are nice and such but...
		\begin{itemize}
			 \item<2-> they are not designed to interoperate seamlessly
			 \item<3-> they are somewhat inflexible
			 \item<4-> they don't fulfill our requirements
		\end{itemize}
		
		\only<5->{If we have to invest time to make existing things working with our ideas, we might just as well do them from scratch exactly how we deem them necessary.}
	\end{frame}
	
	\begin{frame}{Common Policy}
		\begin{itemize}
			\item seperate bundles
			\item common core bundle
			\item combined functionality
		\end{itemize}
		
		Bundles as vertical slices:
		\begin{itemize}
			\item Core bundle (barebone version - everything to extend it)
			\item Functionality bundles (additional application-independent features like rating system, poll support, attachment support)
			\item Application bundles (complete applications - require only core but automatically integrate new functionality)
		\end{itemize}
	\end{frame}
	
	\begin{frame}{Common Policy}
		Common coding style beyond CodeSniffer
		\begin{itemize}
			\item bundles communicate via disclosed APIs only
			\item no assumptions on the input that are not explicitely stated in API documentation
			\item no primitive parameters in public APIs (instead value classes which encapsulate one value and ensure it's integrity and validity, e.g. Username, Password, Address)
			\item explicit classes instead of array for everything (e.g. Queue, List, HashMap)
		\end{itemize}
		This common coding style ensures maximum maintainability and reduces the potential of errors (strings in unexpected and therefore unchecked variations, arrays in unexpected structure (the expected structure could be forgotten in the API documentation)).
	\end{frame}
	
	\subsection{Opportunities}
	
	\begin{frame}{Community}
		Participation
		\begin{itemize}
			\item help shaping the platform (design)
			\item help forming the platform (draft)
			\item help making the platform (implementation)
			\item help testing the platform (quality assurance)
			\item help promoting the platform (marketing)
		\end{itemize}
		
		Be a part in developing a ground-breaking web platform.
	\end{frame}
	
	\begin{frame}{Innovations}
		The architecture allows for faster innovations without breaking existing applications.
		\begin{itemize}
			\item One cool feature that is general-purpose for all web applications? Make it and let every application profit from it.
			\item A better way for user security appears? Implement it without breaking the user base.
			\item You write a better application than existing ones? Users can switch without data loss (content policy).
		\end{itemize}
	\end{frame}
	\begin{frame}{Common Content policy}
		The web platform enforces a strict common content policy. This means that the core data of applications is inter-compatible without loss.
		
		\begin{itemize}
			\item standardized data storage for several content types (e.g. forum categories, boards, threads, posts and forum hierarchy)
			\item leaves room for diversity without putting the admin in a vendor lock-in (staying with current application or lose all or parts of the data)
			\item allows for true competition where the data has no influence
		\end{itemize}
	\end{frame}
	\begin{frame}{Game Integration}
		Due to it's modular nature the web platform could even support integration into an in-game and in-lore browser (as in HTTPS requests from the game to the website running on the platform). This would allow for including real websites into in-lore ``internet''s.
	\end{frame}
	
	\section{Future}
	\begin{frame}{Future}
		\centering Will this platform be finished before Star Citizen goes live?
	\end{frame}
\end{document}

